---
title: "(De/En)coding Experiments"
author: "Karine Pires"
date: "2 Jul 2014"
output: 
  html_document:
    includes:
      after-body: forkme.html
---

Initial Settings
================

## Movie File
For the experiments I used initially [bigbuckbunny](www.bigbuckbunny.org) movie:  
[http://download.blender.org/peach/bigbuckbunny_movies/BigBuckBunny_320x180.mp4]

## Programs
I used ffmpeg on Mac:

```{r, eval=FALSE}
$ ffmpeg --version
ffmpeg version 2.1 Copyright (c) 2000-2013 the FFmpeg developers
  built on Jun 23 2014 16:17:10 with Apple LLVM version 5.1 (clang-503.0.40) (based on LLVM 3.4svn)
```



Decoding
========

Example of decoding:

```{r, eval=FALSE}
$ ffmpeg -i BigBuckBunny_320x180.mp4 -c:v rawvideo -pix_fmt yuv420p -vstats video2_320x180_60FPS_I420.yuv
```


Options   | (from [ffmpeg manual](https://ffmpeg.org/ffmpeg.html))
--------- | --------------------------------------------------------
-i        | input file
-c:v      | -
-pix_fmt  | -
-vstats   | Dump video coding statistics to 'vstats_HHMMSS.log'

vstats dump sample:

```{r, eval=FALSE}
frame=     1 q= 0.0 f_size=  86400 s_size=       84kB time= 156.250 br= 16588.8kbits/s avg_br=     4.4kbits/s type= I
frame=     2 q= 0.0 f_size=  86400 s_size=      169kB time= 312.500 br= 16588.8kbits/s avg_br=     4.4kbits/s type= I
frame=     3 q= 0.0 f_size=  86400 s_size=      253kB time= 468.750 br= 16588.8kbits/s avg_br=     4.4kbits/s type= I
frame=     4 q= 0.0 f_size=  86400 s_size=      338kB time= 625.000 br= 16588.8kbits/s avg_br=     4.4kbits/s type= I
frame=     5 q= 0.0 f_size=  86400 s_size=      422kB time= 781.250 br= 16588.8kbits/s avg_br=     4.4kbits/s type= I
frame=     6 q= 0.0 f_size=  86400 s_size=      506kB time= 937.500 br= 16588.8kbits/s avg_br=     4.4kbits/s type= I
frame=     7 q= 0.0 f_size=  86400 s_size=      591kB time= 1093.750 br= 16588.8kbits/s avg_br=     4.4kbits/s type= I
frame=     8 q= 0.0 f_size=  86400 s_size=      675kB time= 1250.000 br= 16588.8kbits/s avg_br=     4.4kbits/s type= I
frame=     9 q= 0.0 f_size=  86400 s_size=      759kB time= 1406.250 br= 16588.8kbits/s avg_br=     4.4kbits/s type= I
frame=    10 q= 0.0 f_size=  86400 s_size=      844kB time= 1562.500 br= 16588.8kbits/s avg_br=     4.4kbits/s type= I
```


Encoding
========

## With H.264/MPEG-4 AVC = x264

Encoding from raw yuv to h264 with mmpeg:
```{r, eval=FALSE}
$ ffmpeg -f rawvideo -pix_fmt yuv420p -s:v 320x180 -r 60 -i video_320x180_60FPS_I420.yuv -c:v libx264 video.h264.mp4
```

And decoding the video to yuv for comparison:
```{r, eval=FALSE}
$ ffmpeg -i video.h264.mp4 -c:v rawvideo -pix_fmt yuv420p videoh264_320x180_60FPS_I420.yuv
```

## With H.265/High Efficiency Video Coding (HEVC) = x265

```{r, eval=FALSE, echo=FALSE}
$ ffmpeg -i video2_320x180_60FPS_I420.yuv -c:a copy -x265-params crf=25 video_hecv.mov
$ ffmpeg -i INPUT -c:a copy -x265-params crf=25 OUT.mov
```





